Statistical analysis script

### 2023-04-07 code/analysis_code/statistical_analysis.qmd
ml part completed

bag_training_illness
```

@@

bag_training_hosp
```

## Organize Model Performance and Choose the Best One
### Illnesses
```{r}
# Linear Regression
lm_complex_resampled_illness %>%
  collect_metrics()

# Poisson Regression
poisson_complex_resampled_illness %>%
  collect_metrics()

# Random Forest
random_forest_illness_predict %>%
  collect_metrics()

# Make Dataframe of Model RMSEs

@@

### Hospitalizations
```{r}
# Linear Regression
# Poisson Regression
# Random Forest

@@

## Fit Testing Data

>>>>

# Get RMSE
bag_training_illness$err
```

@@

# Get RMSE
bag_training_hosp$err
```

## Organize Model Performance and Choose the Best One
### Illnesses
```{r}
# Make Dataframe of Model RMSEs
illness_model_dataframe <- lm_complex_resampled_illness %>%
  collect_metrics() %>% 
  filter(.metric == "rmse") %>% select(mean) %>% rename(RMSE = mean) %>% 
  mutate(Model = "Linear Regression") %>% 
  full_join(poisson_complex_resampled_illness %>% 
              collect_metrics() %>% 
              filter(.metric == "rmse") %>% select(mean) %>% 
              rename(RMSE = mean) %>% mutate(Model = "Poisson Regression")) %>%
  full_join(random_forest_illness_tuned %>% 
              show_best("rmse") %>% top_n(-1, mean) %>% select(mean) %>%
              rename(RMSE = mean) %>% mutate(Model = "Random Forest")
            ) %>%
  full_join(data.frame(bag_training_illness$err, "Bagging") %>% 
  rename(RMSE = bag_training_illness.err) %>% rename(Model = X.Bagging.)) %>%
  arrange(RMSE)

illness_model_dataframe

@@

### Hospitalizations
```{r}
hosp_model_dataframe <- lm_complex_resampled_hosp %>%
  collect_metrics() %>% 
  filter(.metric == "rmse") %>% select(mean) %>% rename(RMSE = mean) %>% 
  mutate(Model = "Linear Regression") %>% 
  full_join(poisson_complex_resampled_hosp %>% 
              collect_metrics() %>% 
              filter(.metric == "rmse") %>% select(mean) %>% 
              rename(RMSE = mean) %>% mutate(Model = "Poisson Regression")) %>%
  full_join(random_forest_hosp_tuned %>% 
              show_best("rmse") %>% top_n(-1, mean) %>% select(mean) %>%
              rename(RMSE = mean) %>% mutate(Model = "Random Forest")
            ) %>%
  full_join(data.frame(bag_training_hosp$err, "Bagging") %>% 
  rename(RMSE = bag_training_hosp.err) %>% rename(Model = X.Bagging.)) %>%
  arrange(RMSE)

hosp_model_dataframe

@@

Given the above results, the random forest machine learning model is the best model for both health outcomes.

# Modifying Test Data Variables to Maintain Compatibility
```{r}
test_data_final
```

# Fit Testing Data
```{r}
# Illness
placeholder_illnesses <- random_forest_illness_final %>%
  fit(test_data_final) %>% predict(test_data_final)
placeholder_illnesses <- placeholder_illnesses[1:1922, ]

test_data_final %>% select(Illnesses) %>% 
  bind_cols(placeholder_illnesses) %>% rmse(Illnesses, .pred)

# Hospitalizations
placeholder_hosp <- random_forest_hosp_final %>%
  fit(test_data_final) %>% predict(test_data_final)
placeholder_hosp <- placeholder_hosp[1:1922, ]

test_data_final %>% select(Hospitalizations) %>% 
  bind_cols(placeholder_hosp) %>% rmse(Hospitalizations, .pred)
